---
title: "Data605_Assignment13"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Ques-1: Use integration by substitution to solve the integral below:

# $\int$ $4e^{-7x}$ $dx$

# Ans-1: 

 Let, $u = -7x$ 

By taking derivative of u with respect to x we get, 

   $du = -7dx$

or, $dx = -du/7$

 Now, we have, $\int$ $4e^{-7x}$ $dx$

 Putting $-7x = u$ and $dx = -du/7$ we get,

$-4/7$ $\int$ $e^{u}$ $du$

$=$ $-4/7$ $e^{u}$ + $C$

 $=$ $-4/7$ $e^{-7x}$ + $C$


# Ques-2: Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of dN/dt = -3150/ $t^{4}$ - 220 bacteria per cubic centimeter per day, where t is the number of days since treatment began. Find a function N( t ) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter

# Ans-2: 
Given rate, dN/dt = -3150/ $t^{4}$ - 220, integrating the rate equation with respect to time we get,

 $\int$ $dN$ = -3150 $\int$ $t^{-4}$ dt - 220 $\int$ dt 

 $N(t)$ = $3150/3$ $t^{-3}$ - $220t + C$

 $N(1)$=$6530$= $3150/3$ $1^{-3}$ - $220 + C$  [for, t=1, N(1)=6530]

$C= 6530-1050+220$

$C = 5700$

Therefore, the function will be: $N(t)$ = $1050$ $t^{-3}$ - $220t + 5700$


# Ques-3: Find the total area of the red rectangles in the figure below, where the equation of the line is f ( x ) = 2x - 9.

# Ans-3: 
From the given plot we get the lower limit= 4.5 and  the upper limit =8.5. Now, by integrating the given line function within this limits we get the area. Below is the R code for finding the area by doing integration.

```{r}

# define the area function
area_func<-function(x){
  
  return(2*x-9)
}

# Integrate the function over the limits
result<-integrate(area_func, lower = 4.5, upper = 8.5)

result$value
```

# Ques-4: Find the area of the region bounded by the graphs of the given equations.
# $y= x^{2}−2x−2$ , $y=x+2$

# Ans-4: 

Solve the given two equations for x values:

 $x+2 = x^{2}−2x−2$ 

 or, $x^{2}-3x-4 = 0$

 or, $x^{2}-4x+x-4 = 0$

 or, $x(x-4)+1(x-4)=0$

 or, $(x+1) (x-4)=o$

Therefore, $x= -1$ and $x=4$

# define two functions
```{r}

func_1 <- function(x){
  return(x^2 - 2*x -2)
}

func_2 <- function(x){
  return(x +2)
}

```


# plot graphs
```{r}
plot(func_1, -10, 10,ylab = "y")
plot(func_2, -10, 10, add = TRUE)

```

From the plot above, it is seen that the x values at the two curves intersection points are -1 and 4 respectively. We are going to use this values as the lower and upper limits of the integration to find the desired area.

# Find area of the intersection
```{r }
# define function for intersection
inter_func <- function(x){
    return((x+2) - (x^2 - 2*x -2))
}

# find area for bounded by found x limits
area <- integrate(inter_func, lower = -1, upper = 4)
area$value

```


# Ques-5: A beauty supply store expects to sell 110 flat irons during the next year. It costs $3.75 to store one flat iron for one year.There is a fixed cost of $8.25 for each order. Find the lot size and the number of orders per year that will minimize inventory costs.


# Ans-5: 
Let's consider, order quantity, q
                annual demand, d = 110 (targeted sale number)
                holding cost per unit per year, h= 3.75 
                and fixed cost per order, k =8.25

```{r}

# Define the function for calculating total annual inventory cost
total_inventory_cost <- function(q, d= 110, h = 3.75, k= 8.25) {
 
# Calculate annual ordering cost
annual_order_cost<- k* d / q
  
# Calculate annual holding cost
annual_holding_cost<-h * q / 2 # assuming that the average inventory level is half of the order quantity.
  
# Calculate total annual inventory cost
  total_annual_inventory_cost= annual_order_cost +  annual_holding_cost
  
# Return total cost
 return(total_annual_inventory_cost)
}

# Optimization techniques to find the optimal order quantity
optimized_result <- optimize(total_inventory_cost, interval = c(1, 110), d = 110, h = 3.75, k = 8.25)

# Minimum lot size 
optimized_result$minimum

# Minimum total inventory cost
optimized_result$objective

```

Therefore, the lot size that will minimize inventory costs is 22 flat irons, and the number of orders per year will be 110 /22 = 5 orders per year.

# Ques-6: Use integration by parts to solve the integral below:

# $\int$ $ln(9x)x^{6}dx$

# Ans-6: 

Let, $u = ln(9x)$ and, $v = x^{6}$

 So, $du = 1/x dx$

 and $dv = 1/7x^{7}dx$

 Now,
 $\int$ $(uv)dx$ = $ln(9x)∗1/7x^{7}$− $\int$$1/x* 1/7* x^{7}dx$
 
 $\int$ $(uv)dx$ = $ln(9x)∗1/7x^{7}$−1/7$\int$$x^{6}dx$
 
 $\int$ $(uv)dx$ = $ln(9x)∗1/7x^{7}$−$1/49x^{7}+C$

# Ques-7:  Determine whether f( x ) is a probability density function on the interval $[1, e^{6}]$. If not, determine the value of the definite integral, f(x)=1/6x.

# Ans-7: 

$f(x)= 1/6x$

$\int_{1}^{e^{6}}$ $1/6xdx$ 
 
$=$ $1/6$∗$lnx$$|_{1}^{e^{6}}$
 
$=1/6ln(e^{6})−1/6ln(1)$
 
$=1/6[6−0]=1$

The function, $f(x) = 1/(6x)$ is non-negative for all $x$ in $[1, e^{6}]$ and the integral of the function over the given limit is equal to 1. Therefore, the function, f(x) is a probability density function on the given interval.



















